---
title: "Introducing 'annolite'. A Leightweight Fulltext Display and Annotation Toolset"
author: "Andreas Blätte (andreas.blaette@uni-due.de)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{annolite}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
bibliography: references.bib
---


## Purpose

Using large-scale corpora in text-based research comes often evokes the hope that automated content analysis and "distant reading" [@Moretti2013] will facilitate generalizations that can not be attained by the close qualitative analysis of a limited number of texts. Yet as supervised machine learning requires training data that very need to be prepared by way of text annotation, the requirement to work with individual texts is not gone. And if we accept the call to "validate, validate, validate" [@Grimmer2013] to reach sound research results, i.e. to corroborate quantitative findings by qualitative means, those who have a quantitative take on texts still need tools for inspecting and annotating texts qualitatively.

The requirement to integrate quantitative and qualitative approaches to text is not new.  Indeed, there is a breadth of tools for text annotation, or for "coding" texts, as it is mostly called in the social sciences. In the context of information science and computational linguistics, server-based solutions such as brat, WebAnno or INCEpTION are powerful tools for complex text annotation tasks. In the social sciences, ATLAS.ti and MAXQDA dominate the market for the computer-assisted analysis of qualitative data. These are commercial products, to be installed locally, that offer a rich functionality for coding text. So why yet another tool for text analysis?

The open source `annolite` R package offers a leightweight fulltext display and text annotation toolset designed to be used with RStudio. Its functionality is much more limited than the powerful server-based solutions  or the commercial products. But for a set of common, straight-forward text annotation scenarios that have low-level technical requirements - if using the computer for text annotation is essentially like working with printed copies texts using a set of highlighters, possibly writing comments on the margins with a pencil -, `annolite` will offer the functionality that is sufficient. If your annotation task is basic, `annolite` has the advantages that it is is open source, easy to install, and designed to be integrated seamlessly into a pure R workflow.

The technical essence of the package is the htmlwidget `annolite`. The R functionality of the package exposes the htmlwidget (which is written in JavaScript) to the R environment and ensures the communication, i.e. the transfer of data, between R and JavaScript. A shiny gadget launched using the `annotate()` method can be used to annotate a text document within the RStudio environment. The gadget returns a `annotationstable` object which can easily be processed within R. Furthermore, `annolite`  transperency of the research process. The `annolite` htmlwidget can be used to embed the fulltext display of an annotated text in the analysis or the research report you write as an Rmarkdown document. Compared to existing tools for text annotation, the added value of `annolite` is that you have a seamless integration of simple text annotation tasks in a pure R workflow and that you create maximum transparency on the annotation step in a research project by embedding texts and annotations in a html documment written in Rmarkdown.




## Installation and getting started

```{r, eval = TRUE}
library(annolite)
```


## From tidytext to fulltext

```{r, eval = TRUE}
emma_ch1 <- do.call(
  c, lapply(emma_chapters_tokenized[[1]], fulltextlist, element = "p")
)
```

```{r, eval = TRUE}
annolite(
  list(paragraphs = emma_ch1, annotations = annotationstable()),
  dialog = list(choices = dialog_radio_buttons(positive = "green", negative = "red")),
  box = TRUE, width = 650
)
```


## Initialization

We introduce the annolite package by example. In addition to the annolite package, we need the polmineR package which includes the GERMAPARLMINI corpus.

```{r}
library(polmineR)
use("polmineR")
```


## The speech to reconstruct

The example aims at outputting one particular speech. We take a speech held by Voker Kauder in the German Bundestag.

```{r}
P <- partition("GERMAPARLMINI", speaker = "Volker Kauder", date = "2009-11-10")
```


## Input data for the widget

The data that is passed to the JavaScript that generates the output. Expected to be a list of lists that provide data on sections of text. Each of the sub-lists is to be a named list of a character vector with the HTML element the section will be wrapped into, and  a `data.frame` (or a list) with a column "token", and a column "id".

```{r}
D <- fulltextlist(P)
```


## Getting the output

```{r}
annolite(list(paragraphs = D, annotations = NULL), box = TRUE, width = 650)
```


## fulltext functionality

## Getting Started

```{r, eval = TRUE}
library(annolite)
library(polmineR)
library(crosstalk)
```


## From a polmineR subcorpus to fulltext

We introduce the fulltext package by example. In addition to the fulltext package, we need the polmineR package which includes the GERMAPARLMINI corpus.

```{r, eval = TRUE}
library(polmineR)
use("polmineR")
```

The example aims at outputting one particular speech. We take a speech held by Voker Kauder in the German Bundestag.

```{r, eval = TRUE}
sp <- corpus("GERMAPARLMINI") %>% subset(speaker == "Volker Kauder" & date == "2009-11-10")
```

The data that is passed to the JavaScript that generates the output. Expected to be a list of lists that provide data on sections of text. Each of the sub-lists is to be a named list of a character vector with the HTML element the section will be wrapped into, and  a `data.frame` (or a list) with a column "token", and a column "id".

```{r, eval = TRUE}
k <- fulltextlist(sp)
```

So let us see the result ... 

```{r, eval = TRUE}
fulltext(k)
```

```{r}
m <- cpos(sp, query = "Opposition")
anno <- data.frame(color = "yellow", start = m[,1], end = m[,2])
fulltext(k, annotations = anno, box = TRUE)
```

Add a headline

```{r}
h2 <- fulltextlist(c("Volker", "Kauder", "(CDU)"), element = "h2")
fulltext(c(h2, k))
```




## Creating fulltext

```{r, eval = TRUE}
emma_chapters_tokenized2 <- emma_chapters_tokenized
emma_chapters_tokenized2[[1]] <- NULL

emma_chapters <- lapply(
  seq_along(emma_chapters_tokenized2),
  function(i){
    fulltextlist_paras <- lapply(
      emma_chapters_tokenized2[[i]],
      fulltextlist, element = "p"
    )
    y <- do.call(c, fulltextlist_paras)
    name(y) <- sprintf("Chapter %s", i)
    y
  }
)
```


```{r, eval = TRUE}
fulltext(emma_chapters[[1]])
```


## Crosstalking

```{r, eval = TRUE}
fulltext(emma_chapters[1:5])
```


## Perspectives

For complex annotation tasks: INcePTION

I can imagine very well that you could run annolite on a server. 



Enjoy! 